Abstract Plots

### 2021-07-22 Abstract.Rmd
New plots

>>>>

```{r}
vector_to_matrix <- function(mutations.vector){
  tab <- table(mutations.vector)/sum(table(mutations.vector))
  #transform table to a data frame and assign column names to mutations and frequencies
  mutations.df <- data.frame(tab)
  colnames(mutations.df) <- c("mutations", "frequencies")

  #defines a function that joins two data frames and replaces NA with 0
  left_join_NA <- function(x, y, by) {
    left_join(x = x, y = y, by = by) %>% 
      mutate_each(funs(replace(., which(is.na(.)), 0)))
  }

  #converts vector of 96 mutation types to a data frame
  mutation.types.df <- data.frame(mutations)
  #joins together sample probabilities with data frame of mutation types so that all 96 mutation types are included
  complete.mutations.df <- left_join_NA(mutation.types.df, mutations.df, by = "mutations")

  #converts data frame of mutation types and frequencies to a data frame and assigns rownames
  mutations.matrix <- as.matrix(complete.mutations.df$frequencies)
  rownames(mutations.matrix) = mutations

  return(mutations.matrix)
}
```
